---
title: Multiple Correspondence Analysis (MCA) in Educational Data
author: 
- name: "Nirmal Ghimire, Ph.D."
  url: https://www.linkedin.com/in/nirmal-ghimire-5b96a034/
  affiliation: K-16 Literacy Center at University of Texas at Tyler
  affiliation_url: https://www.uttyler.edu/education/literacy-center/
  orcid_id: 0000-0002-2032-1624
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      warning = FALSE,
                      message = FALSE,
                      tidy = 'styler',
                      error = FALSE, 
                      highlight = TRUE, 
                      prompt = FALSE,
                      R.options = list(width = 75))

# Load Libraries
library(tidyverse)
library(ggplot2)
library(janitor)
library(stringr)
library(readr)
library(dplyr)
library(scales)
library(ggthemes)
library(gridExtra)
library(FactoMineR)
library(factoextra)
```

### Introduction 
Multiple Correspondence Analysis (MCA) is a multivariate statistical technique that is used to analyze the relationships between categorical variables. It is a generalization of correspondence analysis (CA), which is used to analyze the relationships between two categorical variables. MCA can be used to explore the associations between multiple categorical variables simultaneously.

MCA works by creating a map of the categorical variables. The map is created by calculating the distances between the different categories of the variables. The closer two categories are on the map, the more similar they are. The further apart two categories are on the map, the less similar they are.

MCA can be used to explore a variety of research questions. For example, MCA can be used to:

* Explore the relationships between different demographic variables, such as age, gender, and education level.
* Explore the relationships between different product features, such as price, color, and size.
* Explore the relationships between different customer segments, such as brand loyalists, price-sensitive shoppers, and impulse buyers.

MCA is a powerful tool that can be used to gain insights into the relationships between categorical variables. It is a versatile technique that can be used to explore a variety of research questions.

## MCA for Analyzing Educational Data:
MCA is particularly well-suited for analyzing educational data, as it can be used to explore a wide range of topics, such as student achievement, teacher effectiveness, and school climate.

One of the key advantages of MCA is its capacity for making comparisons between groups. This feature is beneficial in examining differences in student achievement, teacher effectiveness, or school climate across various groups, such as different genders, races, or socioeconomic backgrounds. By utilizing MCA, educational researchers and policymakers can gain valuable insights into these variations and use them to inform decision-making.

MCA also aids in the identification of underlying dimensions or constructs that contribute to educational outcomes. It uncovers latent variables that may not be directly measured but are critical in understanding educational success. For instance, MCA can reveal associations between variables such as student motivation, parental involvement, and academic achievement. By recognizing these underlying dimensions, educators can design targeted interventions to enhance student engagement and academic performance.

Here are some specific examples of how MCA can be used to analyze educational data:

* MCA can be used to explore the relationship between student achievement and student background characteristics, such as gender, race, or socioeconomic status.
* MCA can be used to identify factors that contribute to teacher effectiveness.
* MCA can be used to compare school climates between different schools.
* MCA can be used to assess the impact of educational interventions.

MCA is a valuable tool for educational researchers and policymakers who are interested in understanding how to improve student achievement. By using MCA, they can identify patterns and relationships in data, and make comparisons between groups. This information can be used to develop and implement effective educational policies and interventions.

```{r data, include=FALSE}
## List of the Variables (after and before Cleaning)
#We are going to use the `raw_data_clean` further modeling. The `raw_data` is the raw version of uploaded data.
raw_data <- read_csv("E:/OneDriveUT Tyler/Desktop/Reading Habits Study Time Diary Survey for Moroccan Teachers/final_data.csv")
# Getting Rid of Second and Third Rows from the Data set
raw_data <- raw_data[-c(2:3), ]
      #names(raw_data)
# Making column names consistent by using clean_names function and saving the data in a new table
raw_data_clean <- raw_data|>
  clean_names()
# Comparing column names after and before cleaning them
names(raw_data_clean)
dim(raw_data_clean)
```

```{r get_input_list, include=FALSE}
## Get the list of all non-NA values in your data
data <- na.omit(unlist(raw_data_clean[c("q8_6_text", "q12_10_text", "q13_11_text", "q14_5_text", "q17_8_text", "q18_7_text", "q20_9_text", "q23_7_text", "q24_6_text", "q27_8_text", "q29_8_text", "q30_6_text", "q33_16_text", "q35_8_text", "q36_6_text")]))

# Convert the list to a table
#data.frame(data)
```


```{r break_data, include=FALSE}
## Breaking the Dataset in Two Different Studies
# create reading_data dataset
reading_data <- raw_data_clean %>%
  select(duration_in_seconds, ip_address, q4, q6, q7, q8, q8_6_text, q12_1:q12_10_text, q13_1:q13_11_text,
         q14, q14_5_text, q15, q16, q17_1:q17_8_text, q18_1:q18_7_text, q19, q20, q20_9_text, q21,
         q22, q23_1:q23_7_text, q24_1:q24_6_text, q25)

# create tv_internet_data dataset
tv_internet_data <- raw_data_clean %>%
  select(duration_in_seconds, ip_address, q4, q6, q7, q8, q8_6_text, q12_1:q12_10_text, q13_1:q13_11_text,
         q26:q37)

# save datasets as CSV files
#write.csv(reading_data, "reading_data.csv", row.names = FALSE)
#write.csv(tv_internet_data, "tv_internet_data.csv", row.names = FALSE)

# Checking the Variables 
names(reading_data)
names(tv_internet_data)
dim(reading_data)
```

```{r getting_rid_of_row_two, include=FALSE}
## Reading Study Data Modeling
reading_data <- read_csv("C:/Users/nghimire/OneDrive - University of Texas at Tyler/Desktop/Reading Habits Study Time Diary Survey for Moroccan Teachers/reading_data.csv")
#str(reading_data)
```

```{r change_class, include=FALSE}
#Changing the variable class
reading_data <- reading_data %>%
      # convert data types
  mutate(
    duration_in_seconds = as.numeric(duration_in_seconds),
    across(q4:q25, as.factor))
#summary(reading_data)
```

```{r get_rid_text}
# Looking at the summary, the variables having `_text` at the end is not useful. Getting rid of them:
new_data <- reading_data %>%
  select(-ends_with("_text"))
#str(new_data)
```

## An Example Workout
### a. Raw Data, Variable Information and Summary
```{r subset_data}
read_data <- reading_data %>%
  select(duration_in_seconds, ip_address,
         q4, q6, q7, q8, q14, q15, q16, 
         q17_1, q17_2, q17_3, q17_4, q17_5, q17_6, q17_7,
         q19, q20, q21, q22, 
         q23_1, q23_2, q23_3, q23_4, q23_5, q23_6, q23_7, q25)
#summary(read_data[ ,-(1:2)])
```

- **Question 4 [q4 - *gender*]**: Response Codes
  Female, Male
- **Question 6 [q6 - *experience*]**: Response Codes
  0-5 years = 0, 6-10 years = 1, 11-years and more = 2
- **Question 7 [q7 - *sch_type*]**: Response Codes
  Rural = 0, Urban/Suburban = 1
- **Question 8 [q8 - *tchr_type*]**: Response Codes
  pre-service = 0, inservice = 1
- **Question 15 [q15 - *rf_time*]**: Response Codes 
- **Question 16 [q16 - *rf_length*]**: Response Codes 
  0 minutes = 0, 15  minutes = 1, 30  minutes = 2, 45  minutes = 3,
  1 hour = 4, 1.5 hours = 5, 2 hours = 6, 3 hours or more = 7
- **Question 17 [q17_1 - *rf_tv*, q17_2 - *rf_music*, q17_3 - *rf_pd*, q17_4 - *rf_write*, q17_5 - *rf_talk_phone*, q17_6 - *rf_onl_game*, q17_7 - *rf_soc_network*]**: Response Codes 
  Never = 0, Alittle of the Time = 1, Some of the Time = 2, Most of the Time = 3
- **Question 19 [q19 - *rf_disp*]**: Response Codes
  No, not at all = 0, Yes, some = 1, Yes, a lot = 2
- **Question 20 [q20 - *ra_text*]**: Response Codes
  Textbook Chapters-Online, Journal articles-Online, Reports-Online, Novels-Online, Textbook Chapters-In   print, Reports-In print, Novels-In print, Other materials-Please specify
- **Question 21 [q21 - *ra_time*]**: Response Codes
  6:00 a.m.-11:59 a.m., Noon-6:00 p.m., 6:00 p.m.-11:59 p.m., Midnight-5:59 a.m.
- **Question 22 [q22 - *ra_length*]**: Response Codes
 0 minutes = 0, 15  minutes = 1, 30  minutes = 2, 45  minutes = 3,
  1 hour = 4, 1.5 hours = 5, 2 hours = 6, 3 hours or more = 7
- **Question 23 [q23_1 - *ra_tv*, q23_2 - *ra_music*, q23_3 - *ra_write*, q23_4 - *ra_talk_phone*, q23_5 - *ra_video_game*, q23_6 - *ra_soc_network*, q23_7 - *ra_other*]**: Response Codes
  Never = 0, A little of the time = 1, Some of the time = 2, Most of the time = 3
- **Question 25 [q25 - *ra_disp*]**: Response Codes 
  No, not at all = 0, Yes, some = 1, Yes, a lot = 2
  
```{r preparing_variables}
# Question 6
read_data$q6 <- factor(
  ifelse(read_data$q6 %in% c("0 teaching experience", "1-5 years"), 0,
    ifelse(read_data$q6 %in% c("11-15 years","16 - 20", "20+"), 2,
      ifelse(read_data$q6 == "6-10 years", 1,read_data$q6)
        )
  ),
  levels = c(0, 1, 2),
  labels = c("0-5 years", "6-10 years", "11-years and more")
)
  #summary(read_data$q6)

# Question 7
read_data$q7 <- factor(
  ifelse(read_data$q7 == "Click to write Choice 4", NA,
    ifelse(read_data$q7 %in% c("Urban", "Suburban"), 1,
      ifelse(read_data$q7 == "Rural", 0, read_data$q7)
    )
  ),
  levels = c(0, 1),
  labels = c("Rural", "Urban/Suburban")
  )
    #summary(read_data$q7)

# Question 8
read_data$q8 <- factor(ifelse(
  read_data$q8 == "I am a pre-service teacher (i.e., I am currently in training at ​Centre régional des métiers de l’éducation et de la formation (CRMEF) or Ecole Normale Supérieure (ENS)",
  0,
  ifelse(
    read_data$q8 == "I am an-service teacher (i.e., I am currently working full-time as a teacher)",
    1,
    NA
  )
), levels = c(0, 1), labels = c("pre-service", "inservice"))
    #summary(read_data$q8)

# Question 14
# Create a function to extract the first selection
read_data$q14 <- as.character(read_data$q14)
extract_first_selection <- function(text) {
  selections <- strsplit(text, ",")[[1]]
  first_selection <- trimws(selections[1])
  return(first_selection)
}
# Apply the function to create a new variable with the first selection
read_data$q14_first_selection <- sapply(read_data$q14, extract_first_selection)
# Recode the first selection into the desired categories
read_data$q14_recode <- factor(
  read_data$q14_first_selection,
  levels = c("News stories online", "Social media threads (e.g., Face book, Instagram, Twitter, etc.)", "Books online", "Magazines online", "Newspapers-In print", "Magazines-In print", "Other Materials in print (please specify)"),
  labels = c("News stories online", "Social media threads", "Books online", "Magazines online", "Newspapers-In print", "Magazines-In print", "Other Materials in print (please specify)")
)
# Remove the intermediate variable 
 read_data$q14_first_selection <- NULL
# Change the class of the Variable
 read_data$q14_recode <- as.factor(read_data$q14_recode)
  #summary(read_data$q14_recode)

# Question 16
read_data$q16 <- factor(recode(read_data$q16,
  "0 minutes" = 0,
  "15  minutes" = 1,
  "30  minutes" = 2,
  "45  minutes" = 3,
  "1 hour" = 4,
  "1.5 hours" = 5,
  "2 hours" = 6,
  "3 hours or more" = 7
))
# Convert to factor with the specified levels
levels(read_data$q16) <- c("0 minutes", "15 minutes", "30 minutes", "45 minutes", "60 minutes", "90 minutes", "120 minutes", "180 minutes or more")
    #summary(read_data$q16)
    #summary(as.numeric(read_data$q16))

# Re-coding Responses in Question 17(q17_2, q17_3, q17_4, q17_5, q17_6, q17_7) 
# Function
recodelikert <- function(data, variables, categories) {
  for (variable in variables) {
    data[[variable]] <- recode(data[[variable]], !!!categories)
    data[[variable]] <- as.factor(data[[variable]])
  }
  return(data)
}
# Defining Categories
categories <- list(
  "Never" = 0,
  "Alittle of the Time" = 1,
  "Some of the Time" = 2,
  "Most of the Time" = 3
)
read_data <- recodelikert(read_data, c("q17_1", "q17_2", "q17_3", "q17_4", "q17_5", "q17_6", "q17_7"), categories)

# Questions 23 (q23_1, q23_2, q23_3, q23_4, q23_5, q23_6, q23_7)
# Defining Categories
categories_1 <- list(
  "Never" = 0,
  "A little of the time" = 1,
  "Some of the time" = 2,
  "Most of the time" = 3
)
read_data <- recodelikert(read_data, c("q23_1", "q23_2", "q23_3", "q23_4", "q23_5", "q23_6", "q23_7"), categories_1)

# Question 19, and saving as q19_recode
read_data$q19_recode <- factor(
  ifelse(read_data$q19 %in% c("Did not multi-task", "Not sure"), NA,
         ifelse(read_data$q19 == "No, not at all", 0,
                ifelse(read_data$q19 == "Yes, some", 1,
                       ifelse(read_data$q19 == "Yes, a lot", 2, read_data$q19)
                )
         )
  ),
  levels = c(0, 1, 2),
  labels = c("No, not at all", "Yes, some", "Yes, a lot"),
  exclude = NULL
)

# Question 20
read_data$q20 <- as.character(read_data$q20)
# Apply the function to create a new variable with the first selection
read_data$q20_first_selection <- sapply(read_data$q20, extract_first_selection)
# Recode the first selection into the desired categories
read_data$q20_recode <- factor(
  read_data$q20_first_selection,
  levels = c("Textbook Chapters-Online", "Journal articles-Online", "Reports-Online", "Novels-Online
", "Textbook Chapters-In print", "Reports-In print", "Novels-In print", "Other materials-Please specify"),
  labels = c("Textbook Chapters-Online", "Journal articles-Online", "Reports-Online", "Novels-Online", "Textbook Chapters-In print", "Reports-In print", "Novels-In print", "Other materials-Please specify")
)
# Remove the intermediate variable
read_data$q20_first_selection <- NULL

# Question 21
read_data$q21 <- as.character(read_data$q21)
# Apply the function to create a new variable with the first selection
read_data$q21_first_selection <- sapply(read_data$q21, extract_first_selection)
# Recode the first selection into the desired categories
read_data$q21_recode <- factor(
  read_data$q21_first_selection,
  levels = c("6:00 a.m.-11:59 a.m.", "Noon-6:00 p.m.", "6:00 p.m.-11:59 p.m.", "Midnight-5:59 a.m."),
  labels = c("6:00 a.m.-11:59 a.m.", "Noon-6:00 p.m.", "6:00 p.m.-11:59 p.m.", "Midnight-5:59 a.m.")
)
# Remove the intermediate variable
read_data$q21_first_selection <- NULL

# Question 22
read_data$q22 <- factor(recode(read_data$q22,
  "0 minutes" = 0,
  "15 minutes" = 1,
  "30 minutes" = 2,
  "45 minutes" = 3,
  "1 hour" = 4,
  "1.5 hours" = 5,
  "2 hours" = 6,
  "3 hours or more" = 7
))
# Convert to factor with the specified levels
levels(read_data$q22) <- c("0 minutes", "15 minutes", "30 minutes", "45 minutes", "60 minutes", "90 minutes", "120 minutes", "180 minutes or more")

# Question 25 and Saving as q25_recode
read_data$q25_recode <- factor(
  ifelse(read_data$q25 %in% c("Did not multi-task", "Not sure"), NA,
         ifelse(read_data$q25 == "No, not at all", 0,
                ifelse(read_data$q25 == "Yes, some", 1,
                       ifelse(read_data$q25 == "Yes, a lot", 2, read_data$q25)
                )
         )
  ),
  levels = c(0, 1, 2),
  labels = c("No, not at all", "Yes, some", "Yes, a lot"),
  exclude = NULL
)

#summary(read_data[,-2])
#str(read_data)
```


```{r changing_names}
read_data <- read_data %>%
  rename(gender = q4,
         experience = q6,
         sch_type = q7,
         tchr_type = q8,
         rf_text = q14_recode,
         rf_time = q15,
         rf_length = q16,
         rf_tv = q17_1,
         rf_music = q17_2,
         rf_pd = q17_3,
         rf_write = q17_4,
         rf_talk_phone = q17_5,
         rf_onl_game = q17_6,
         rf_soc_network = q17_7,
         rf_disp = q19_recode,
         ra_text = q20_recode,
         ra_time = q21_recode,
         ra_length = q22,
         ra_tv = q23_1,
         ra_music = q23_2,
         ra_write = q23_3,
         ra_talk_phone = q23_4,
         ra_video_game = q23_5,
         ra_soc_network = q23_6,
         ra_other = q23_7,
         ra_disp = q25_recode)
#summary(read_data[,-2])
#str(read_data)
```


```{r media_dem}
## 1. Investigating the Relationship Between Displacement and Demographic Factors:
# Cross-tabulation of rf_disp and gender
rf_disp_gender_xtab <- xtabs(~ rf_disp + gender, data = read_data)
# Calculate percentage values with two decimal places
rf_disp_gender_xtab_percentage <- round(prop.table(rf_disp_gender_xtab, margin = 2) * 100, 2)
#rf_disp_gender_xtab_percentage

# Cross-tabulation of ra_disp and gender
ra_disp_gender_xtab <- xtabs(~ ra_disp + gender, data = read_data)
# Calculate percentage values with two decimal places
ra_disp_gender_xtab_percentage <- round(prop.table(ra_disp_gender_xtab, margin = 2) * 100, 2)
#ra_disp_gender_xtab_percentage

# Cross-tabulation of rf_disp and experience
rf_disp_experience_xtab <- xtabs(~ rf_disp + experience, data = read_data)
# Calculate percentage values with two decimal digits
rf_disp_experience_xtab_percentage <- round(prop.table(rf_disp_experience_xtab, margin = 2) * 100, 2)
#rf_disp_experience_xtab_percentage

# Cross-tabulation of rf_disp and experience
ra_disp_experience_xtab <- xtabs(~ ra_disp + experience, data = read_data)
# Calculate percentage values with two decimal places
ra_disp_experience_xtab_percentage <- round(prop.table(ra_disp_experience_xtab, margin = 2) * 100, 2)
#ra_disp_experience_xtab_percentage

# Cross-tabulation of rf_disp and school type
rf_disp_sch_type_xtab <- xtabs(~ rf_disp + sch_type, data = read_data)
# Calculate percentage values with two decimal places
rf_disp_sch_type_xtab_percentage <- round(prop.table(rf_disp_sch_type_xtab, margin = 2) * 100, 2)
#rf_disp_sch_type_xtab_percentage

# Cross-tabulation of ra_disp and school type
ra_disp_sch_type_xtab <- xtabs(~ ra_disp + sch_type, data = read_data)
# Calculate percentage values with two decimal places
ra_disp_sch_type_xtab_percentage <- round(prop.table(ra_disp_sch_type_xtab, margin = 2) * 100, 2)
#ra_disp_sch_type_xtab_percentage

# Cross-tabulation of rf_disp and teacher type
rf_disp_tchr_type_xtab <- xtabs(~ rf_disp + tchr_type, data = read_data)
rf_disp_tchr_type_xtab_percentage <- round(prop.table(rf_disp_tchr_type_xtab, margin = 2) * 100, 2)
#rf_disp_tchr_type_xtab_percentage

# Cross-tabulation of rf_disp and teacher type
ra_disp_tchr_type_xtab <- xtabs(~ ra_disp + tchr_type, data = read_data)
#ra_disp_tchr_type_xtab
# Calculate percentage values with two decimal places
ra_disp_tchr_type_xtab_percentage <- round(prop.table(ra_disp_tchr_type_xtab, margin = 2) * 100, 2)
#ra_disp_tchr_type_xtab_percentage
```


```{r rf_disp, out.width="100%"}
# Filter out NAs from the dataset
filtered_data <- read_data[complete.cases(read_data), ]

# Create the grouped bar plots
gender_rf_disp <- ggplot(filtered_data, aes(x = rf_disp, fill = gender)) +
  geom_bar(position = "dodge", color = "black") +
  labs(x = "Reading for Fun Displacement", y = "Frequency") +
  scale_y_continuous(breaks = NULL) +  # Remove y-axis ticks
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank(),  # Remove y-axis ticks
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 12, face = "bold")) +
  scale_fill_manual(values = c("#0072B2", "#E69F00"),
                    labels = c("Female", "Male"))

gender_ra_disp <- ggplot(filtered_data, aes(x = ra_disp, fill = gender)) +
  geom_bar(position = "dodge", color = "black") +
  labs(x = "Reading for Academic Purposes", y = "") +
  scale_y_continuous(breaks = NULL) +  # Remove y-axis ticks
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank(),  # Remove y-axis ticks
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 10),
        plot.title = element_text(size = 12, face = "bold")) +
  scale_fill_manual(values = c("#0072B2", "#E69F00"),
                    labels = c("Female", "Male"))

# Arrange the plots side by side
grid.arrange(gender_rf_disp, gender_ra_disp, ncol = 2)
```

***Note: Please, do not take away anything from the plot. I created it just for fun. It doesn't show anything meaningful.*** 

```{r}
final_data <- read_data|>
  dplyr::select(gender, experience, sch_type,
                tchr_type, rf_time, rf_length, 
                rf_tv, rf_music, rf_pd, rf_write,
                rf_talk_phone, rf_onl_game, rf_soc_network,
                ra_length, ra_tv, ra_music, ra_write, 
                ra_talk_phone, ra_video_game, ra_soc_network, 
                ra_other, rf_text, rf_disp, ra_text,
                ra_time, ra_disp)
#dim(final_data)
#str(final_data)
#names(final_data)
summary(read_data)
```

## A. Reading for Academic Purposes

```{r preparing_data_for_MCA}
ra_data <- final_data[, c("experience", "sch_type", "ra_time", "ra_length", "ra_tv", "ra_music", "ra_talk_phone", "ra_video_game", "ra_soc_network", "ra_disp")]
ra_data <- na.omit(ra_data)
```

### i. Perform the MCA
```{r perform_MCA}
mca_result <- MCA(ra_data, graph = TRUE)
```

### ii. Print the results
Create a dimension plot to visualize the positions of categories and variables in the MCA solution space. This plot helps understand the relationships between variables and identify patterns or clusters. The categories and variables that are closer together on the plot are more strongly associated.

```{r print_result}
print(mca_result)
fviz_mca_var(mca_result, axes = c(1, 2), col.var = "contrib", gradient.cols = c("blue", "white", "red"))
```

### iii. Extract the weights of the columns
These weights reflect the relative importance of each variable in the MCA analysis. Variables with higher weights have a stronger influence on the analysis, while variables with lower weights have less impact.

```{r extract_weights}
weights <- mca_result$call$marge.col

### iv. Create a data frame to store the weights and variable names
weights_df <- data.frame(variable = names(weights), weight = weights)

# Sort the data frame in descending order of weights
weights_df <- weights_df[order(weights_df$weight, decreasing = TRUE), ]

# Print the sorted data frame
print(weights_df)
```

### iv. Eigenvalues
```{r eigenvalues}
# Extract the eigenvalues
eigenvalues <- mca_result$eig

# Round the eigenvalues to two decimal places
rounded_eigenvalues <- round(eigenvalues, 3)

# Print the rounded eigenvalues
print(rounded_eigenvalues)
```

### v. Contributions of variables to dimensions (Inertia)
Assess the relationships between variables and dimensions. Variables that have higher associations (higher cosine similarity) with specific dimensions are more strongly related to those dimensions. This information can help identify the variables that contribute most to each dimension and understand the underlying patterns in the data.

```{r var_contribution_to_dimension}
var_contributions <- mca_result$var$contrib
rounded_contributions <- round(mca_result$var$contrib, 3)
# Sort the rounded contributions in descending order
#sorted_contributions <- sort(rounded_contributions, decreasing = TRUE)
# Print the sorted contributions
#print(sorted_contributions)
print(rounded_contributions)
```

A factor analysis was conducted to examine the underlying dimensions of the variables. The analysis revealed five distinct dimensions (Dim 1 to Dim 5) that accounted for the variability in the data. Each dimension appears to represent a unique pattern of variables. Notably, Dim 1 showed moderate positive loadings for variables related to 11-years and more, indicating a potential relationship between this age group and other factors. Dim 2 showed a mix of positive and negative loadings for various variables, suggesting a complex relationship between them. Dim 3 exhibited higher loadings for variables related to specific time intervals, indicating a potential temporal association. Dim 4 showed a mix of loadings for different variables, suggesting a diverse pattern of associations. Dim 5 demonstrated higher loadings for variables related to 'Yes, a lot,' potentially indicating a strong association with this response category. Further analysis and contextual information are required to provide a comprehensive interpretation of these dimensions.

### vi. Coordinates of categories
Calculate the category contributions to each dimension. Category contributions indicate the extent to which a particular category contributes to the overall structure of each dimension. Higher contributions suggest that the category has a stronger association with that dimension.

```{r cat_coordinates}
categories_coordinates <- mca_result$var$coord
round(categories_coordinates,3)
```

### vii. Plotting the results as a biplot
A biplot, which combines the dimension plot with the variable plot. This plot allows you to visualize both the relationships between categories and the relationships between variables in the same plot. It helps interpret the associations between categories, variables, and dimensions simultaneously. This can lead to a better understanding of the relationships and provide valuable information for further analysis or decision-making.

```{r extract_result_explore_output, out.width="100%"}
plot.MCA(mca_result, cex = 0.8)
```

### ix. Calculate Chi-square Statistics
```{r chi-squre}
eigenvalues_m <- mca_result$eig
chi_square_stats <- eigenvalues_m^2
df <- 1  # Degrees of freedom for each dimension
p_values <- 1 - pchisq(chi_square_stats, df)


for (i in seq_along(chi_square_stats)) {
  cat("Dimension", i, "Chi-square:", chi_square_stats[i], "df:", df, "p-value:", p_values[i], "\n")
}
```

### viii. Single Dimension Plot and Corresponding Variable Contribution
The red dotted line provides a visual reference point for interpreting the significance of variable contributions in relation to the expected distribution. Variables with contributions significantly above or below this line are the ones that are contributing the most to the variation along the specific dimension.

* Above the Red Dotted Line: If a variable's contribution bar is above the red dotted line, it indicates that the observed distribution of that variable's categories is contributing more than expected to the variation in the specific dimension. In other words, the variable's category distribution is not uniform across levels of the dimension and is contributing disproportionately to the dimension.
* Below the Red Dotted Line: Conversely, if a variable's contribution bar is below the red dotted line, it suggests that the variable's category distribution is contributing less than expected to the variation in the dimension. This indicates that the variable's category distribution is more uniform across levels of the dimension.

```{r var_contribution_plot}
library(factoextra)

# Extract the variable contributions for each dimension
var_contributions <- mca_result$var$contrib

# Create separate plots for each dimension
for (dim in 1:5) {
  plot_title <- paste("Contribution of Variables to Dimension", dim)
  
  # Create the contribution plot for the current dimension
  p <- fviz_contrib(mca_result, choice = "var", axes = c(dim), gradient.cols = c("blue", "white", "red")) +
    ggtitle(plot_title)
  
  # Display the plot
  print(p)
}
```

